Active Learning for SAT Solver Benchmarking {\large (extended and revised version)}

### 2024-05-28 paper_jar/paper.tex
Minor changes

\begin{table}[tb]
	\centering
	\caption{Test-set prediction performance for predicting solver timeouts (a binary target) with different prediction models.}
	\label{tab:timeout-prediction}
	~\\[1em]
	\begin{tabular}{lcc}
		\toprule
		\multirow[c]{2}{*}{Timeout Prediction Models} & \multicolumn{2}{c}{Average MCC ($\pm$ std)} \\
		\cmidrule(lr){2-3}
		& {Without Runtime Feat.} & {With Runtime Feat.} \\
		\midrule
		Stacking (QDA\,+\,RF)                 & 0.6513 ($\pm$ 0.0458) & 0.9527 ($\pm$ 0.0292) \\[0.4ex]
		Quadratic Discriminant Analysis (QDA)                    & 0.2593 ($\pm$ 0.1310) & 0.9290 ($\pm$ 0.0339) \\[0.4ex]
		Random Forest (RF)         & 0.6607 ($\pm$ 0.0547) & 0.8530 ($\pm$ 0.0479) \\[0.4ex]
		AdaBoost                             & 0.5412 ($\pm$ 0.0612) & 0.8384 ($\pm$ 0.0444) \\[0.4ex]
		Decision Tree                         & 0.5980 ($\pm$ 0.0423) & 0.8059 ($\pm$ 0.0707) \\[0.4ex]
		Logistic Regression                   & 0.2031 ($\pm$ 0.0728) & 0.8052 ($\pm$ 0.1018) \\[0.4ex]
		$k$NN                   & 0.5108 ($\pm$ 0.0387) & 0.7885 ($\pm$ 0.1521) \\[0.4ex]
		Multilayer Perceptron                      & 0.1293 ($\pm$ 0.0718) & 0.7760 ($\pm$ 0.1408) \\[0.4ex]
		Support Vector Machine               & 0.0595 ($\pm$ 0.0554) & 0.7757 ($\pm$ 0.2149) \\[0.4ex]
		Naive Bayes                           & 0.1173 ($\pm$ 0.0872) & 0.7306 ($\pm$ 0.1394) \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\begin{table}[tb]
  \centering
  \caption{Test-set prediction performance for predicting the $C_k$ cluster labels (a discrete target) with the best-performing models.}
  \label{tab:cluster-prediction}
  \begin{tabular}{lcc}
    \toprule
    \multirow[c]{2}{*}{$C_3$ Cluster Prediction Models} & \multicolumn{2}{c}{Average MCC ($\pm$ std)} \\
    \cmidrule(lr){2-3}
    & {Without Clustering Feat.} & {With Clustering Feat.} \\
    \midrule
    Stacking (QDA\,+\,RF)                 & 0.7464 ($\pm$ 0.0497) & 0.8380 ($\pm$ 0.0634) \\[0.4ex]
    Quadratic Discriminant Analysis (QDA)                     & 0.6903 ($\pm$ 0.0607) & 0.7738 ($\pm$ 0.0459) \\[0.4ex]
    Random Forest (RF)         & 0.7116 ($\pm$ 0.0385) & 0.7841 ($\pm$ 0.0469) \\[0.4ex]
    \midrule
    \multirow[c]{2}{*}{$C_4$ Cluster Prediction Models} & \multicolumn{2}{c}{Average MCC ($\pm$ std)} \\
    \cmidrule(lr){2-3}
    & {Without Clustering Feat.} & {With Clustering Feat.} \\
    \midrule
    Stacking (QDA\,+\,RF)                 & 0.6562 ($\pm$ 0.0538) & 0.7366 ($\pm$ 0.0377) \\[0.4ex]
    Quadratic Discriminant Analysis (QDA)                     & 0.6007 ($\pm$ 0.0765) & 0.6872 ($\pm$ 0.0469) \\[0.4ex]
    Random Forest (RF)         & 0.6033 ($\pm$ 0.0455) & 0.6828 ($\pm$ 0.0527) \\[0.4ex]
    \midrule
    \multirow[c]{2}{*}{$C_5$ Cluster Prediction Models} & \multicolumn{2}{c}{Average MCC ($\pm$ std)} \\
    \cmidrule(lr){2-3}
    & {Without Clustering Feat.} & {With Clustering Feat.} \\
    \midrule
    Stacking (QDA\,+\,RF)                 & 0.5835 ($\pm$ 0.0615) & 0.6396 ($\pm$ 0.0553) \\[0.4ex]
    Quadratic Discriminant Analysis (QDA)                      & 0.5508 ($\pm$ 0.0669) & 0.5881 ($\pm$ 0.0912) \\[0.4ex]
    Random Forest (RF)         & 0.5420 ($\pm$ 0.0459) & 0.5895 ($\pm$ 0.0475) \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{figure}[tb]
  \centering
  \resizebox{0.85\textwidth}{!}{
    \graphicspath{{plots/}}
    \input{plots/anni_final_families.pgf}
  }
  \caption{
    Scatter plot illustrating the relative importance of different instance families for ranking on the full dataset. The x-axis depicts the frequency of instance families in the dataset, while the y-axis represents the average frequency in the samples selected by active learning. The dashed line represents families that occur with the same frequency in the dataset and samples. Results are on the full dataset with cross-validation over all solvers.
  }
  \label{fig:annifinalfamilies}
\end{figure}

>>>>

\begin{table}[tb]
	\centering
	\caption{Test-set prediction performance for predicting solver timeouts (a binary target) with different prediction models.}
	\label{tab:timeout-prediction}
	~\\[1em]
	\begin{tabular}{lcc}
		\toprule
		\multirow[c]{2}{*}[-0.27em]{Timeout Prediction Models} & \multicolumn{2}{c}{Average MCC ($\pm$ std)} \\
		\cmidrule(lr){2-3}
		& {Without Runtime Feat.} & {With Runtime Feat.} \\
		\midrule
		Stacking (QDA\,+\,RF)                 & 0.6513 ($\pm$ 0.0458) & 0.9527 ($\pm$ 0.0292) \\[0.4ex]
		Quadratic Discriminant Analysis (QDA)                    & 0.2593 ($\pm$ 0.1310) & 0.9290 ($\pm$ 0.0339) \\[0.4ex]
		Random Forest (RF)         & 0.6607 ($\pm$ 0.0547) & 0.8530 ($\pm$ 0.0479) \\[0.4ex]
		AdaBoost                             & 0.5412 ($\pm$ 0.0612) & 0.8384 ($\pm$ 0.0444) \\[0.4ex]
		Decision Tree                         & 0.5980 ($\pm$ 0.0423) & 0.8059 ($\pm$ 0.0707) \\[0.4ex]
		Logistic Regression                   & 0.2031 ($\pm$ 0.0728) & 0.8052 ($\pm$ 0.1018) \\[0.4ex]
		$k$NN                   & 0.5108 ($\pm$ 0.0387) & 0.7885 ($\pm$ 0.1521) \\[0.4ex]
		Multilayer Perceptron                      & 0.1293 ($\pm$ 0.0718) & 0.7760 ($\pm$ 0.1408) \\[0.4ex]
		Support Vector Machine               & 0.0595 ($\pm$ 0.0554) & 0.7757 ($\pm$ 0.2149) \\[0.4ex]
		Naive Bayes                           & 0.1173 ($\pm$ 0.0872) & 0.7306 ($\pm$ 0.1394) \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\begin{table}[tb]
  \centering
  \caption{Test-set prediction performance for predicting the $C_k$ cluster labels (a discrete target) with the best-performing models.}
  \label{tab:cluster-prediction}
  \begin{tabular}{lcc}
    \toprule
    \multirow[c]{2}{*}[-0.27em]{$C_3$ Cluster Prediction Models} & \multicolumn{2}{c}{Average MCC ($\pm$ std)} \\
    \cmidrule(lr){2-3}
    & {Without Clustering Feat.} & {With Clustering Feat.} \\
    \midrule
    Stacking (QDA\,+\,RF)                 & 0.7464 ($\pm$ 0.0497) & 0.8380 ($\pm$ 0.0634) \\[0.4ex]
    Quadratic Discriminant Analysis (QDA)                     & 0.6903 ($\pm$ 0.0607) & 0.7738 ($\pm$ 0.0459) \\[0.4ex]
    Random Forest (RF)         & 0.7116 ($\pm$ 0.0385) & 0.7841 ($\pm$ 0.0469) \\[0.4ex]
    \midrule
    \multirow[c]{2}{*}[-0.27em]{$C_4$ Cluster Prediction Models} & \multicolumn{2}{c}{Average MCC ($\pm$ std)} \\
    \cmidrule(lr){2-3}
    & {Without Clustering Feat.} & {With Clustering Feat.} \\
    \midrule
    Stacking (QDA\,+\,RF)                 & 0.6562 ($\pm$ 0.0538) & 0.7366 ($\pm$ 0.0377) \\[0.4ex]
    Quadratic Discriminant Analysis (QDA)                     & 0.6007 ($\pm$ 0.0765) & 0.6872 ($\pm$ 0.0469) \\[0.4ex]
    Random Forest (RF)         & 0.6033 ($\pm$ 0.0455) & 0.6828 ($\pm$ 0.0527) \\[0.4ex]
    \midrule
    \multirow[c]{2}{*}[-0.27em]{$C_5$ Cluster Prediction Models} & \multicolumn{2}{c}{Average MCC ($\pm$ std)} \\
    \cmidrule(lr){2-3}
    & {Without Clustering Feat.} & {With Clustering Feat.} \\
    \midrule
    Stacking (QDA\,+\,RF)                 & 0.5835 ($\pm$ 0.0615) & 0.6396 ($\pm$ 0.0553) \\[0.4ex]
    Quadratic Discriminant Analysis (QDA)                      & 0.5508 ($\pm$ 0.0669) & 0.5881 ($\pm$ 0.0912) \\[0.4ex]
    Random Forest (RF)         & 0.5420 ($\pm$ 0.0459) & 0.5895 ($\pm$ 0.0475) \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{figure}[tb]
  \centering
  \resizebox{0.75\textwidth}{!}{
    \graphicspath{{plots/}}
    \input{plots/anni_final_families.pgf}
  }
  \caption{
    Scatter plot illustrating the relative importance of different instance families for ranking on the full dataset. The x-axis depicts the frequency of instance families in the dataset, while the y-axis represents the average frequency in the samples selected by active learning. The dashed line represents families that occur with the same frequency in the dataset and samples. Results are on the full dataset with cross-validation over all solvers.
  }
  \label{fig:annifinalfamilies}
\end{figure}
